\vspace{6mm}\bfseries\LARGE Energy-Aware Planning-Scheduling for Autonomous Aerial Robots

### 2022-07-12 energy-planning.tex
fixed the affiliation

%% author names and affiliations
\author{
  Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{3}}$, and Ulrik Pagh Schultz$^{\text{3}}$
  \thanks{The work was partly funded by EU grant \textnumero 779882 (TeamPlay). The work for H.\hspace*{.4ex}G. is supported by the Ramon y Cajal grant \textnumero RYC2020-030090-I.}
  \thanks{$^{\text{1}}$A.\hspace*{.4ex}S. is with the Department of Mechanical Engineering and Material Science, Yale University, CT, USA, but the work was performed while affiliated with the\hspace*{.6ex}SDU\hspace*{.4ex}UAS. Email: {\tt\footnotesize \href{mailto:adam.seewald@yale.edu}{adam.seewald@yale.edu}};}
  \thanks{$^{\text{2}}$H.\hspace*{.4ex}G. is with the Department of Computer Architecture and Technology and with CITIC, University of Granada, Spain;} 
  \thanks{$^{\text{3}}$H.\hspace*{.3ex}S.\hspace*{.3ex}M.,\hspace*{.5ex}U.\hspace*{.3ex}P.\hspace*{.3ex}S. are with the\hspace*{.5ex}SDU\hspace*{.3ex}UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 
  University of Southern Denmark.}
}

@@

{\color{black}
The performance metric is $\Sigma_{t\in\mathcal{T}}{\small (w_1c_{i,1}(t)+w_2c_{i,2}(t))}/$ $\small {\small |\mathcal{T}|\text{SoC}(t_f)}$. If the initial battery SoC %at $t_0$ 
is seventy percent and both the parameters are weighted equally, i.e., ${\small w_1=w_2=}$ one half, \hyperref[fig:trajs-I-static]{I} would not be able to complete the flight, and \hyperref[fig:trajs-II-static]{II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
Nonetheless, performance metrics of \hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-dyn-ii]{ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx. 45 and 35 percent for \hyperref[fig:trajs-dyn-i]{i}, and 62 and 87 percent for \hyperref[fig:trajs-dyn-ii]{ii}.}
For both cases, scaling factors are derived empirically %, 
{\color{black}similarly to $\delta_i$ set to two hundred fifty}, 
the horizon $N$ is set to six seconds {\color{black} as in} relevant literature~\cite{gavilan2015iterative,%kang2009linear,
stastny2018nonlinear%,chao2011collision
}, order $r$ is three% (see Fig.~\ref{fig:il-abs})
, and the matrices $Q,R,Q_f$ are chosen such that the cost is merely 
squared control. {\color{black} $h$ is set to one-hundredth of a second and to one second for $\mathcal{K}$ and $\mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
%\subsection{Algorithm evaluation}
%\subsubsection*{Periodic energy model}
%The figure
%{\color{black} Fig.~\hyperref[fig:stat]{6c}} %further 
%details the energy model's estimate (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}$), power ($\Upsilon$), and period ($T$). % We motivate this choice again with Fig.~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate. 
%The {\color{black} right} detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods suffice for a consistent %state 
%estimate. %With non-periodic signals, we observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others. It hence approximates the non-periodicity with a linear model.

>>>>

%% author names and affiliations
\author{
  Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{3}}$, and Ulrik Pagh Schultz$^{\text{3}}$
  \thanks{The work was partly funded by EU grant \textnumero 779882 (TeamPlay). The work for H.\hspace*{.4ex}G. is supported by the Ramon y Cajal grant \textnumero RYC2020-030090-I.}
  \thanks{$^{\text{1}}$A.\hspace*{.4ex}S. is with the Department of Mechanical Engineering and Material Science, Yale University, CT, USA, but the work was performed while affiliated with SDU UAS. Email: {\tt\footnotesize \href{mailto:adam.seewald@yale.edu}{adam.seewald@yale.edu}};}
  \thanks{$^{\text{2}}$H.\hspace*{.4ex}G. is with the Department of Computer Architecture and Technology and with CITIC, University of Granada, Spain;} 
  \thanks{$^{\text{3}}$H.\hspace*{.3ex}S.\hspace*{.3ex}M.,\hspace*{.5ex}U.\hspace*{.3ex}P.\hspace*{.3ex}S. are with SDU UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 
  University of Southern Denmark.}
}

@@

{\color{black}
The performance metric is $\Sigma_{t\in\mathcal{T}}(${\small $(w_1c_{i,1}(t)+w_2c_{i,2}(t)$}$)/$ $(${\small $|\mathcal{T}|\text{SoC}(t_f)$}$)$. If the initial battery SoC %at $t_0$ 
is seventy percent and both the parameters are weighted equally, i.e., ${\small w_1=w_2=}$ one half, \hyperref[fig:trajs-I-static]{I} would not be able to complete the flight, and \hyperref[fig:trajs-II-static]{II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
Nonetheless, performance metrics of \hyperref[fig:trajs-dyn-i]{i} and \hyperref[fig:trajs-dyn-ii]{ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx. 45 and 35 percent for \hyperref[fig:trajs-dyn-i]{i}, and 62 and 87 percent for \hyperref[fig:trajs-dyn-ii]{ii}.}
For both cases, scaling factors are derived empirically %, 
{\color{black}similarly to $\delta_i$ set to two hundred fifty}, 
the horizon $N$ is set to six seconds {\color{black} as in} relevant literature~\cite{gavilan2015iterative,%kang2009linear,
stastny2018nonlinear%,chao2011collision
}, order $r$ is three% (see Fig.~\ref{fig:il-abs})
, and the matrices $Q,R,Q_f$ are chosen such that the cost is merely 
squared control. {\color{black} $h$ is set to one-hundredth of a second and to one second for $\mathcal{K}$ and $\mathcal{T}$ respectively to allow sufficient precision and re-planning online.}
%\subsection{Algorithm evaluation}
%\subsubsection*{Periodic energy model}
%The figure
%{\color{black} Fig.~\hyperref[fig:stat]{6c}} %further 
%details the energy model's estimate (see detail view for \hyperref[fig:ener:static-I]{I}--\hyperref[fig:ener:static-II]{II}) on an initial slice of the model (${\hat{y}}$), power ($\Upsilon$), and period ($T$). % We motivate this choice again with Fig.~\ref{fig:il-abs}, where the power spectrum subfigure shows that 3 frequencies are adequate. 
%The {\color{black} right} detail of \hyperref[fig:ener:static-I]{I} illustrates the evolutions of the state $\mathbf{q}$ in time, concluding that approximately two periods suffice for a consistent %state 
%estimate. %With non-periodic signals, we observed that the estimator estimates primarily the first state $\alpha_0$ and it neglects the others. It hence approximates the non-periodicity with a linear model.
